### 2016-06-27 ch05-initvals/tables/timings.tbl.tex
Small corrections in Ch05 + some requested ones

\pgfplotstabletypeset[zerofill=true,string replace={nan}{},precision=0,relative*=0,empty cells with={\deemph{--}}, %round to 1 ms
    columns/method/.style={string type,column type=l,column name={\textsc{Method}}},
    columns/Q/.style={column type=c,column name={$Q\axisunit{dB}$},zerofill=false},
    columns/NBW/.style={column type=c,column name={$N_{3\unit{dB}}$},zerofill=false},
    columns/tsmooth/.style={column type=r,column name={$t_{\mathrm{smooth}} \axisunit{ms}$},multiply by=1000},
    columns/tinit/.style={column type=r,column name={$t_{\mathrm{init}} \axisunit{ms}$},multiply by=1000},
    columns/tfinal/.style={column type=r,column name={$t_{\mathrm{final}} \axisunit{ms}$},multiply by=1000},
]{%
Q  NBW  method  tsmooth    tinit  tfinal
 % 6  36  \model{\trueSymbol}    nan     nan     0.197034 
 % 6  36  \model{exist}   nan     nan     0.159937 
 6  36  \model{trunc}   0.745073    0.0623485   0.163107 
 6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
 % 6  48  \model{\trueSymbol}    nan     nan     0.209216 
 % 6  48  \model{exist}   nan     nan     0.206823 
 6  48  \model{trunc}   1.00383     0.0902347   0.208173 
 6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
% 20  36  \model{\trueSymbol}    nan     nan     0.445936 
% 20  36  \model{exist}   nan     nan     0.429752 
20  36  \model{trunc}   4.83667     0.225876    0.454757 
20  36  \model{RFIR}    6.92575     0.253981    0.482431 
% 20  48  \model{\trueSymbol}    nan     nan     0.467081 
% 20  48  \model{exist}   nan     nan     0.457577 
20  48  \model{trunc}   6.59726     0.312937    0.461114 
20  48  \model{RFIR}    8.05168     0.312297    0.468905 
}

>>>>

\pgfplotstabletypeset[zerofill=true,string replace={nan}{},precision=0,relative*=0,empty cells with={\deemph{--}}, %round to 1 ms
    columns/method/.style={string type,column type=l,column name={\textsc{Method}}},
    columns/Q/.style={column type=c,column name={$Q\axisunit{dB}$},zerofill=false},
    columns/NBW/.style={column type=c,column name={$\nBW$},zerofill=false},
    columns/tsmooth/.style={column type=r,column name={$t_{\mathrm{smooth}} \axisunit{ms}$},multiply by=1000},
    columns/tinit/.style={column type=r,column name={$t_{\mathrm{init}} \axisunit{ms}$},multiply by=1000},
    columns/tfinal/.style={column type=r,column name={$t_{\mathrm{final}} \axisunit{ms}$},multiply by=1000},
]{%
Q  NBW  method  tsmooth    tinit  tfinal
 % 6  36  \model{\trueSymbol}    nan     nan     0.197034 
 % 6  36  \model{exist}   nan     nan     0.159937 
 6  36  \model{trunc}   0.745073    0.0623485   0.163107 
 6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
 % 6  48  \model{\trueSymbol}    nan     nan     0.209216 
 % 6  48  \model{exist}   nan     nan     0.206823 
 6  48  \model{trunc}   1.00383     0.0902347   0.208173 
 6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
% 20  36  \model{\trueSymbol}    nan     nan     0.445936 
% 20  36  \model{exist}   nan     nan     0.429752 
20  36  \model{trunc}   4.83667     0.225876    0.454757 
20  36  \model{RFIR}    6.92575     0.253981    0.482431 
% 20  48  \model{\trueSymbol}    nan     nan     0.467081 
% 20  48  \model{exist}   nan     nan     0.457577 
20  48  \model{trunc}   6.59726     0.312937    0.461114 
20  48  \model{RFIR}    8.05168     0.312297    0.468905 
}
